Towards a Cognitive System That Can Recognize Spatial Regions Based on Context

### 2012-01-25 scenarios/cdsr/trunk/papers/AAAI2012/evaluation.tex
eval

To determine how people define CDRSs, we asked three na\"ive users to draw polygons for each region type for each room. This task was performed using a webpage (link removed for blind review) shown in the inset in Figure~\ref{fig:ug40} on which each user was presented with an image of the real room plus the map data generated by the robot (as in Figure~\ref{fig:rooms}) onto which the drawing could be done. The user-defined polygons define the \textit{target regions} against which we evaluate our transfers.

We consider a \textit{problem instance} to be a room and a sought CDSR type. For each room containing a manually encoded CDSR of the sought type, we generate an \textit{transferred region} using analogical transfer. To assess the quality of the transfer, we calculate precision ($p$, the proportion of the transferred region that overlaps with the target region) and recall ($r$, the proportion of the target region that overlaps with the transferred region) as follows:

@@

Using this approach we generate results showing the matches between each of the following pairs of regions: the transferred region and the appropriate target region; the manually encoded CDSR and target region; and the region for the whole room and the target region. 
Results comparing transferred and target regions measure how well our system is able apply a single example to new situations. The comparisons between the manual annotations to the target regions measure how well the anchor points we chose capture the users' regions (who were not constrained to anchor points). Results from the whole room regions provide a baseline performance for comparison.

@@

These results support the hypothesis that anchor points can provide a symbolic representation on top of sensor data for context-dependent spatial regions, and, when combined with qualitative spatial relations, they facilitate learning from a single example through analogical transfer. Collaboration with human users requires a high precision and recall, because cognitive systems must be able to understand as well as refer to these regions in human environments. Consequently, the high manually encoded precisions and recalls indicate that the defined anchor points are a reasonable starting place for a symbolic representation. Our future work seeks to further evaluate the utility of this representation by embedding the cognitive system within tasks with human users.

The transferred regions were considerably more precise (.47) when compared to the room as whole (.17), and their recalls (.46) indicate that they captured almost half of the area indicated by the human user. Our approach performed the best when the extent of the context dependent spatial region is closely tied to objects as is the case in the front rows of the classroom with p's of .76 and .82 for the inferred and the manually encoded regions respectively. The system performs worst when the extent of the CDSR is defined as an unbounded area near or around particular objects. The office of a studio apartment is loosely defined as the region around the desk. This motivates one direction of future work to expand the vocabulary of anchor points to better capture these notions of space.

>>>>

To determine how people define CDRSs, we asked three na\"ive users to draw polygons for each region type for each room. This task was performed using a webpage on which each user was presented with an image of the real room plus an image of the map data generated by the robot onto which the drawing could be done. The webpage (link removed for blind review) is shown in the inset in Figure~\ref{fig:ug40}. The user-defined polygons define the \textit{target regions} against which we evaluate our transfers.

We consider a \textit{problem instance} to be a room and a sought CDSR type. For each room containing a manually encoded CDSR of the sought type, we generate a \textit{transferred region} using analogical transfer. To assess the quality of the transfer, we calculate precision ($p$, the proportion of the transferred region that overlaps with the target region) and recall ($r$, the proportion of the target region that overlaps with the transferred region) as follows:

@@

Using this approach we generate results showing the matches between each of the following pairs of regions: the transferred region and the appropriate target region; the CDSR we manually encoded for the target room and target region; and the region for the whole room and the target region. 
Results comparing transferred and target regions measure how well our system is able apply a single example to new situations. The comparisons between the manual annotations to the target regions measure how well the anchor points we chose capture the users' regions (who were not constrained to anchor points). Results from the whole room regions provide a baseline performance for comparison.

@@

These results support the hypothesis that anchor points can provide a symbolic representation on top of sensor data for context-dependent spatial regions, and, when combined with qualitative spatial relations, they facilitate learning from a single example through analogical transfer. Collaboration with human users requires a high precision and recall, because cognitive systems must be able to understand as well as refer to these regions in human environments. Consequently, the high manually encoded precisions and recalls indicate that the defined anchor points are a reasonable starting point for a symbolic representation. Our future work seeks to further evaluate the utility of this representation by embedding the cognitive system within tasks with human users.

The transferred regions were considerably more precise (.47) when compared to the room as whole (.17), and their recalls (.46) indicate that they captured almost half of the area indicated by the human user. As we create CDSRs using anchor points defined on perceived entities, our approach performs best when the boundary of the target CDSR is closely tied to such entities. This is the case in the front rows of the classroom, with $p$ of .76 and .82 for the inferred and the manually encoded regions respectively. The system performs worst when the extent of the CDSR is defined as an unbounded area near or around particular objects. The office of a studio apartment is loosely defined as the region around the desk. This motivates one direction of future work:  expanding the vocabulary of anchor points to better capture these notions of space.
